Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-28 main.tex
Update on Overleaf.

We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
Since $\Omega$ is connected, this is equivalent to  
\begin{align}
    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align}
We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
\\

@@

\begin{align}

@@

We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where we use an upper bound by Chua and Wheeden:
\begin{align}
    C_{{\rm P},{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{{\rm PF},{\rm EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align}
When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
\begin{align}\label{math:l1estimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{1}(\Omega)}
    \leq 
    \frac{ \diam(\Omega) }{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    .
\end{align}
When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
\begin{gather*}
    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align}
\end{subequations}
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
These mappings are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below.

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
\\

@@

    \todo{Complete the estimate.}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
        We begin with the following preparatory observations. 
        Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
        We let $A_{T} \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
        That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
        Then the mapping 
        \begin{align}
            F_T(x) 
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x
        maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
        \begin{align}
            F_T^{-1}(x) 
            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x
        We analyze its Lipschitz properties.
        In what follows, $y \in \bbR^{n}$. 
        On the one hand, 
        we compute the Jacobian at any $x \in \mathring T$:
            \Jacobian F_T(x) \cdot y
            \frac{ \|x\| y - x \|x\|^{-1} x^t y }{\|x\|^2} 
            \left( \vecone \cdot A_{T}^{-1} x \right)
            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} y \right)
            \left( \Id - \|x\|^{-2} x \otimes x^t \right)
            \frac{ 1 }{ \|x\| } 
            \left( \vecone \cdot A_{T}^{-1} x \right)
            \frac{x}{\|x\|} \left( \vecone \cdot A_{T}^{-1} x \right)
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \left( \Id - \hat x \otimes \hat x^t \right) y
            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
        This is an orthogonal sum of two vectors. Its norm satisfies:
            \| \Jacobian F_T(x) \cdot y \|^{2}
            \left| A_{T}^{-t} \vecone \cdot \hat x \right|^{2}
            \| \left( \Id - \hat x \otimes \hat x^t \right) y \|^{2}
            \left| A_{T}^{-t} \vecone \cdot y \right|^{2} \| \hat x \|^{2}
        The Euclidean operator norm satisfies 
            \| \Jacobian F_T(x) \| 
            \sqrt 2 \left\| A_{T}^{-t} \vecone \right\|_{2}
            \sqrt{2n} \cdot \sigma_{\max}(A_{T}^{-1}) 
        On the other hand, we can rewrite the Jacobian as:
            \Jacobian F_T(x) \cdot y
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \left( \hat x \otimes \hat x^t \right) y
            \left( A_{T}^{-t} \vecone \cdot y \right) \hat x 
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x^{t}
                \vecone^{t} A_{T}^{-1} 
            \right) y
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
                A_{T}^{-t} \vecone
            \right)^{t} y
        Its inverse is found via the Woodbury formula: 
        % Its inverse is easily verified to be:
            \Jacobian F_T(x)^{-1}
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
            \Id
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-2}
            \hat x 
                \left( A_{T}^{-t} \vecone \cdot \hat x \right) \hat x
                A_{T}^{-t} \vecone
            \right)^{t} 
            \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                \Id
                \hat x 
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
                    \hat x
                    \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    A_{T}^{-t} \vecone
                \right)^{t}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \Id
                \hat x 
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right)^{-1}
                    % \left( A_{T}^{-t} \vecone \cdot \hat x \right) 
                    \hat x
                    \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                    A_{T}^{-t} \vecone
                \right)^{t}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \Id - \hat x \otimes \hat x^{t}
                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \hat x \otimes \vecone^{t} A_{T}^{-1}
        The inverse acts via multiplication with $\left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}$ on the span of $\hat x$.
        We notice the upper bound 
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
            \| A_{T}^{-1} \hat x \|^{-1}_{1}
            \| A_{T}^{-1} \hat x \|^{-1}_{2}
            \sigma_{\min}( A_{T}^{-1} )^{-1}
            \sigma_{\max}( A_{T} )
        This holds because $A_{T}^{-1} \hat x$ is in the positive quadrant.
        %, and its scalar product with $\vecone$ is minimized when it is colinear with a coordinate axis.
        If $y \in \bbR^{n}$ is orthogonal to $\hat x$, then 
            \| \Jacobian F_T(x)^{-1} \cdot y \|^{2}
%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
%             \left\| 
%                 y
%             \right\|^{2}
%             \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
%             \left| 
%                 \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
%                 \vecone^{t} A_{T}^{-1} y 
%             \right|^{2}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-2}
            \left\| 
            \right\|^{2}
                \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{-1}
                \vecone^{t} A_{T}^{-1} y 
            \right|^{2}
            \left( \vecone \cdot A_{T}^{-1} \hat x \right)^{2}
        The operator norm of that inverse is:
            \| \Jacobian F_T(x)^{-1} \|
            \sigma_{\max}( A_{T} )
            \left( 1 + n \frac{ \sigma_{\max}(A_{T})^{2} }{ \sigma_{\min}(A_{T})^{2} } \right)^{\frac 1 2}
        Since the domain and codomain of $F_{T}$ are convex, 
        this also implies bounds on the Lipschitz constants of $F_{T}$ and its inverse.

        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

        \item 
        We construct a new triangulation that contains $T$ and that is a star around $S$.
        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of $T$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

@@

@@

        % \todo{Combine all this to get the final transformation.}
        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
        Using our initial observations, we obtain homeomorphisms 
            \Psi_{\calK } : |\calK| \rightarrow \calB,
            \qquad 
            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.

@@

            \Xi_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta

@@

        We estimate the Jacobians: 
            \| \Jacobian \Xi_{S} \| 
            \sup_{ K \in \calK  }
            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
            \sigma_{\max}(A_{K}) 
            \sup_{ K \in \calR' } 
            \sqrt{2n} 
            \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \calR  } \kappa(A_{K})
            \| \Jacobian \Xi_{S}^{-1} \| 
            \sup_{ K \in \calK  }
            \sqrt{2n} 
            \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \calR' } 
            \left( 1 + n \kappa(A_{K})^{2} \right)^{\frac 1 2}
            \sigma_{\max}(A_{K}) 
            \sup_{ K \in \calR  } \kappa(A_{K})
        \color{red}

>>>>

We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
Since $\Omega$ is connected, this is equivalent to  
\begin{align*}
    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
\\

@@

@@

We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where we use an upper bound by Chua and Wheeden:
\begin{align*}
    C_{{\rm P},{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align*}
Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align*}
    C_{{\rm PF},{\rm EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align*}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align}
When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
\begin{align}\label{math:l1estimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{1}(\Omega)}
    \leq 
    \frac{ \diam(\Omega) }{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    .
\end{align}
When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
\begin{gather*}
    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align*}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align*}
\end{subequations}
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
These mappings are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below.

@@

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
\\

@@

    \todo{Complete the estimate.}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

        \item 
        We let $z'_{S}$ be the midpoint of $S'$. 
        We first define a new triangulation $\calS$ by the barycentric refinement of the complementary $S'$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

@@

        The last simplicial complex that we introduce is called $\calK$,
        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.

@@

        We introduce a bi-Lipschitz mapping 
            \Psi : |\calR'| \rightarrow |\calK|
        in the following manner. Let $T \in \calR'$ be an $n$-dimensional simplex and let $x \in T$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.
        We define 
            \Psi(x) 
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse 
            \Psi^{-1}(x) 
            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} } x
        We analyze its Jacobian. 
        First, by assumption,
            \Psi(x) 
            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x
        In what follows, $y \in \bbR^n$. We observe 
            \Jacobian \Psi(x) \cdot y 
                ( A_{T}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot x )
                ( A_{T}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot x )^2
            x
            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y
                ( A_{T}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )
            x
                ( A_{T}^{-t} \vecone \cdot x )
                ( A_{K}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )^2
            x
            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } y
                ( A_{T}^{-t} \vecone \cdot y ) 
                ( A_{K}^{-t} \vecone \cdot  x )
            x
            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 
                    ( A_{K}^{-t} \vecone \cdot y ) 
                    ( A_{K}^{-t} \vecone \cdot  x ) 
                x
        The vector $A_{K}^{-1} x$ has length at least $\sigma_{\min}( A_{K}^{-1} ) \| x \|$ and the product with $\vecone$ is smallest when the vector is colinear with one of the coordinate axes. We conclude that 
        \[
             A_{K}^{-t} \vecone \cdot x 
             \vecone \cdot A_{K}^{-1} x 
             \geq 
             \sigma_{\min}( A_{K}^{-1} ) \| x \|.
        \]
        Together with the Xu-Zikatanov inequality, we obtain the upper bound 
            \| \Jacobian \Psi(x) \|
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }
            1
            n
            \frac{ \sigma_{\max}( A_{T}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }
        By completely analogous arguments, we find 
            \| \Jacobian \Psi(x) \|
            \sqrt{n}
            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{T}^{-1} ) }
            1
            n
            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{T}^{-2} ) }

@@

            \Xi := \Psi \circ \Theta

@@

        It preserves the interface from $T$ onto $U$. 
        It is continuous and bi-Lipschitz due to Rademacher's theorem.

        \item 
        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
        Each bisection step reduces the diameter by at most a factor of one half,
        and it reduces the volume always by a factor of one half. 
        We use the estimates in Lemma~\ref{lemma:affinetransform}.
        This shows
